---
title: "Base de Connaissance"
author: "Nomena"
date: "09/03/2021"
output:
  html_document: default
  pdf_document: default
params:
  goal: tex
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown Chunk

### Chunk name

```` ```{r by-name} ```` for chunk name: can set up networks of cached
chunks to avoid re-performing expensive computations on every run.

### Chunk options

`eval = FALSE` prevents code from being evaluated. This is useful for
displaying example code, or for disabling a large block of code without
commenting each line.

`include = FALSE` runs the code, but doesn't show the code or results in
the final document. Use this for setup code that you don't want
cluttering your report.

`echo = FALSE` prevents code, but not the results from appearing in the
finished file. Use this when writing reports aimed at people who don't
want to see the underlying R code.

`message = FALSE` or `warning = FALSE` prevents messages or warnings
from appearing in the finished file.

`results = 'hide'` hides printed output; `fig.show = 'hide'` hides
plots.

`error = TRUE` causes the render to continue even if code returns an
error.It's also useful if you're teaching R and want to deliberately
include **an error**.

## Table

```{r}
knitr::kable(
  mtcars[1:5, ], 
  caption = "A knitr kable."
)
```

For even deeper customisation, consider the **xtable, stargazer, pander,
tables, and ascii packages**.

## Caching

It can be painful if you have some computations that take a long time.
The solution is `cache = TRUE`.

`dependson = "raw_data"` should contain a character vector of every
chunk that the cached chunk depends on. Knitr will update the results
for the cached chunk whenever it detects that one of its dependencies
have changed.

regularly clear out all your caches with `knitr::clean_cache()`.

## GLobal options

    ```{r, eval=FALSE}`r ''`
    knitr::opts_chunk$set(
      comment = "#>",
      collapse = TRUE
    )
    ```

uses my preferred comment formatting, and ensures that the code and
output are kept closely entwined

    ```{r, eval=FALSE}`r ''`
    knitr::opts_chunk$set(
      echo = FALSE
    )

    ```

For report: only showing the chunks you deliberately choose to show
(with `echo = TRUE`).

## Inline Code

    `r`

to embed R code into an R Markdown document: directly into the text

## YAML header

### Parameters

Parameters are useful when you want to re-render the same report with
distinct values for various key inputs.

For example, you might be producing sales reports per branch, exam
results by student, or demographic summaries by country

This example uses a `my_class` parameter to determine which class of
cars to display:

    ---
    output: html_document
    params:
      my_class: "suv"
    ---

    ```{r setup, include = FALSE}`r ''`
    library(ggplot2)
    library(dplyr)

    class <- mpg %>% filter(class == params$my_class)
    ```

    # Fuel economy for `r params$my_class`s

    ```{r, message = FALSE}`r ''`
    ggplot(class, aes(displ, hwy)) + 
      geom_point() + 
      geom_smooth(se = FALSE)
    ```

You can write atomic vectors directly into the YAML header. You can also
run arbitrary R expressions by prefacing the parameter value with !r

    params:
      start: !r lubridate::ymd("2015-01-01")
      snapshot: !r lubridate::ymd_hms("2015-01-01 12:30:00")

<http://rmarkdown.rstudio.com/developer_parameterized_reports.html#parameter_user_interfaces>

`purrr:pwalk()` for advanced

## Bibliographies and Citations

To use this feature, specify a bibliography file using the bibliography
field in your file's header. The field should contain a path from the
directory that contains your .Rmd file to the file that contains the
bibliography file:

    bibliography: rmarkdown.bib

To create a citation within your .Rmd file, use a key composed of '\@' +
the citation identifier from the bibliography file.

You can change the style of your citations and bibliography by
referencing a CSL (citation style language) file in the csl field:

    bibliography: rmarkdown.bib
    csl: apa.csl

<http://github.com/citation-style-language/styles>

## R Markdown formats

    title: "Viridis Demo"
    output: html_documen

    rmarkdown::render("diamond-sizes.Rmd", output_format = "word_document")

YAML param:

    title: "Viridis Demo"
    output: html_document

    rmarkdown::render("diamond-sizes.Rmd", output_format = "word_document")

**Documents :** - pdf_document : PDF with LaTeX - word_document :
Microsoft Word documents (.docx). - odt_document : OpenDocument Text
documents (.odt). - rtf_document : Rich Text Format (.rtf) documents -
md_document : Markdown document. This isn't typically useful by itself,
but you might use it if, for example, your corporate CMS or lab wiki
uses markdown. - github_document: this is a tailored version of
md_document designed for sharing on GitHub.

For `html_documents` another option is to make the code chunks hidden by
default, but visible with a click:

    output:
      html_document:
        code_folding: hide

**Notebooks :** - html_notebook: focused on collaborating with other
data scientists Emailing .nb.html files is a simple way to share
analyses with your colleagues. But things will get painful as soon as
they want to make changes

    output:
      html_notebook: default
      github_document: default

**Presentation** - `ioslides_presentation` : HTML presentation with
ioslide - `slidy_presentation` : HTML presentation with W3C Slidy -
`beamer_presentation` : PDF presentation with LaTeX Beamer

-   `revealjs::revealjs_presentation` - HTML presentation with reveal.js
-   `rmdshower`, <https://github.com/MangoTheCat/rmdshower>, provides a
    wrapper around the shower, <https://github.com/shower/shower>,
    presentation engine

**Dashboards** Flexdashboard makes it particularly easy to create
dashboards using R Markdow.

    ---
    title: "Diamonds distribution dashboard"
    output: flexdashboard::flex_dashboard
    ---

    ```{r setup, include = FALSE}`r ''`
    library(ggplot2)
    library(dplyr)
    knitr::opts_chunk$set(fig.width = 5, fig.asp = 1/3)
    ```

## Using Python

```{python}

import numpy
import pandas

```

Add Chunk Python

| Col1 | Col2 | Col3 |
|------|------|------|
|      |      |      |
|      |      |      |
|      |      |      |

## Auto format and add table

`bout de code` ok

| Col1 | Col2   | Col3 |
|------|--------|------|
| var1 | **go** |      |
|      |        |      |
|      |        |      |

: Table my

```{r}
library(dplyr)
mtcars%>%
  group_by(cyl, vs)
```

In the global options panel, you can now enable the rainbow parenthesis
options:

## Brackets

```{r}
(((((((())))))))
```
